---
title: "**OBSERVING COVID-19 CASES**"
author: "*Eric Nguyen*"
date: "*2024-10-11*"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **General Introduction of the Project**
#### Introduction
[...]

#### Purpose
[...]

#### Future Developments
[...]

#### Libraries used
`readr`, `dplyr`, `tibble`

### **Implementing**
#### Loading libraries
``` {r echo = TRUE}
library(readr)
library(dplyr)
library(tibble)
```

#### Import the csv file
``` {r echo = TRUE}
covid_df <- read.csv("C:\\Users\\nguye\\Documents\\Coding\\Personal Projects\\R\\Observing Covid-19 Cases\\covid19.csv")
```

#### Dimension of the dataset
``` {r echo = TRUE}
dimension <- dim(covid_df)
dimension
```

#### Column names of the dataset
``` {r echo = TRUE}
vector_cols <- colnames(covid_df)
vector_cols
```

#### Filter `All States` from the dataset
``` {r echo = TRUE}
covid_df_all_states <- covid_df %>%
  filter(Province_State == "All States") %>%
  select(-Province_State)
head(covid_df_all_states, 10)
```

#### Select daily measures
``` {r echo = TRUE}
covid_df_all_states_daily <- covid_df_all_states %>%
  select(c(
    Date,
    Country_Region,
    active,
    hospitalizedCurr,
    daily_tested,
    daily_positive
  ))
head(covid_df_all_states_daily, 10)
```

#### Extracting top 10 countries with most cases
``` {r echo = TRUE}
covid_df_all_states_daily_sum <- covid_df_all_states_daily %>%
  group_by(Country_Region) %>%
  summarise(
    tested = sum(daily_tested),
    positive = sum(daily_positive),
    active = sum(active),
    hospitalized = sum(hospitalizedCurr)
  ) %>%
  arrange(desc(tested))
covid_top_10 <- head(covid_df_all_states_daily_sum, 10)
covid_top_10
```

#### Identifying the highest positive against tested cases
``` {r echo = TRUE}
countries <- covid_top_10$Country_Region
tested_cases <- covid_top_10$tested
positive_cases <- covid_top_10$positive
active_cases <- covid_top_10$active
hospitalized_cases <- covid_top_10$hospitalized

names(tested_cases) <- countries
names(positive_cases) <- countries
names(active_cases) <- countries
names(hospitalized_cases) <- countries

positive_cases/tested_cases

positive_tested_top_3 <- c(
  "United Kingdom" = 0.113,
  "United States" = 0.109,
  "Turkey" = 0.081
)
positive_tested_top_3
```

#### Keeping relevant information
``` {r echo = TRUE}
united_kingdom <- c(0.11, 1473672, 166909, 0, 0)
united_states <- c(0.10, 17282363, 1877179, 0, 0)
turkey <- c(0.08, 2031192, 163941, 2980960, 0)

covid_mat <- rbind(united_kingdom, united_states, turkey)

colnames(covid_mat) <- c("Ratio", "tested", "positive", "active", "hospitalized")
covid_mat
```

#### Putting all together
``` {r echo = TRUE}
question <-
"Which countries have had the highest number of positive cases against the number of tests?"

answer <-
c("Positive tested cases" = positive_tested_top_3)

datasets <- list(
  original = covid_df,
  allStates = covid_df_all_states,
  allStatesDaily = covid_df_all_states_daily,
  top_10 = covid_top_10
)

matrices <- list(covid_mat)

vectors <- list(vector_cols, countries)

data_structure_list <- list("dataframe" = datasets, "matrix" = matrices, "vector" = vectors)

covid_analysis_list <- list(question, answer, data_structure_list)

covid_analysis_list[[2]]
```